\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2018-06-04 write_up/mixfishsim_ecolmod.tex
Parallelisation testing using omp - no obvious benefit

Use of spatial management as a tool has been proposed as a method to reduce
discards \added[id=PD]{\citep{Holmes2011, Little2014, Dunn2014a}}. However, its
implementation is hampered by lack of knowledge of fish and fishery
spatiotemporal dynamics and understanding of the scale at which processes are
important for management. Understanding the correct scale for spatial
management is crucial in order to implement measures at a resolution that
ensures effective management \citep{Dunn2016} while minimising economic impact.
For example, a scale that promotes species avoidance for vulnerable or low
quota species while allowing continuance of sustainable fisheries for available
quota species. \\

Ensuring measures are implemented at an appropriate scale has been a challenge
in the past that has led to ineffectual measures with unitended consequences
such as limited impact towards the management objective or increased benthic
impact on previously unexploited areas (e.g. the cod closure in the North
Sea \citep{Rijnsdorp2001,Dinmore2003}). Since then more refined spatial
information has become available through the combination of logbook and Vessel
Monitoring System (VMS) data \citep{Lee2010, Bastardie2010, Gerritsen2012,
	Mateo2016} and more real-time spatial management has been possible 
	\citep[e.g.][]{Holmes2011}. Such information is, however, patchy and
derived from an inherently biased sampling programme (i.e. targeted fishing).
Further, fishers generally only recorded landings (not catch) on a daily
basis\todo{\added[id=JJ]{Its not clear what the problem is: landings
		collected on daily basis or landings recorded rather than catch}}.
This leads to questions about the validity of inference that can be drawn from
landings data assigned to VMS activity pings\todo{\added[id=JJ]{This comes as a
	surprise: I thought this was going to be about discards}}. \\

@@

We simulate a fishery closure to protect one species based on the
fishery-dependent inferred distributions at a spatial and temporal scale
typical in fisheries management, and assess a theoretical "benefit" to the
population, and effect on the other three populations\todo{\added[id=JJ]{If
		the paper has two goals this should be clear from the start,
		but may be better over 2 MSs}}. Further, we extend our analysis
to a range of spatial and temporal scales to assess the impact of these
processes on the success of the management measure. \\

@@

%\textcolor{gray}{[Guidance: Provide sufficient details to allow the work to be
%reproduced by an independent researcher. Methods that are already published
%should be summarized, and indicated by a reference.  If quoting directly from a
%previously published method, use quotation marks and also citep the source. Any
%modifications to existing methods should also be described.] \\ }
%
\replaced[id=PD]{A}{We developed and implemented a simulation model with a}
modular event-based \replaced{simulation model was developed with}{approach,
	where} \added[id=PD]{sub-}modules \deleted[id=PD]{are} implemented on
independent time-scales appropriate to capture the characteristic of the
\replaced[id=PD]{different processes}{process modelled} (Figure 1).
\added[id=PD]{The following sub-modules were included to capture the full
	system: 1) Population dynamics, 2) Recruitment dynamics, 3) Population
	movement, 4) fishery dynamics.} \\

>>>>

Use of spatial management as a tool has been proposed as a method to reduce
discards \added[id=PD]{\citep{Holmes2011, Little2014, Dunn2014a}}. However, its
implementation is hampered by lack of knowledge of fish and fishery
spatiotemporal dynamics and understanding of the scale at which processes are
important for management. Understanding the correct scale for spatial
management is crucial in order to implement measures at a resolution that
ensures effective management \citep{Dunn2016} while minimising economic impact.
For example, a scale that promotes species avoidance for vulnerable or low
quota species while allowing continuance of sustainable fisheries for available
quota species.\\

Ensuring measures are implemented at an appropriate scale has been a challenge
in the past that has led to ineffectual measures with unitended consequences
such as limited impact towards the management objective or increased benthic
impact on previously unexploited areas (e.g. the cod closure in the North
Sea \citep{Rijnsdorp2001,Dinmore2003}). Since then more refined spatial
information has become available through the combination of logbook and Vessel
Monitoring System (VMS) data \citep{Lee2010, Bastardie2010, Gerritsen2012,
	Mateo2016} and more real-time spatial management has been possible 
	\citep[e.g.][]{Holmes2011}. Such information is, however, patchy and
derived from an inherently biased sampling programme (i.e. targeted fishing).
Further, fishers generally only recorded landings (not catch) on a daily
basis\todo{\added[id=JJ]{Its not clear what the problem is: landings
		collected on daily basis or landings recorded rather than catch}}.
This leads to questions about the validity of inference that can be drawn from
landings data assigned to VMS activity pings\todo{\added[id=JJ]{This comes as a
	surprise: I thought this was going to be about discards}}.\\

@@

We simulate a fishery closure to protect one species based on the
fishery-dependent inferred distributions at a spatial and temporal scale
typical in fisheries management, and assess a theoretical "benefit" to the
population, and effect on the other three populations\todo{\added[id=JJ]{If
		the paper has two goals this should be clear from the start,
		but may be better over 2 MSs}}. Further, we extend our analysis
to a range of spatial and temporal scales to assess the impact of these
processes on the success of the management measure.\\

@@

%\textcolor{gray}{[Guidance: Provide sufficient details to allow the work to be
%reproduced by an independent researcher. Methods that are already published
%should be summarized, and indicated by a reference.  If quoting directly from a
%previously published method, use quotation marks and also citep the source. Any
%modifications to existing methods should also be described.] \\ }
%
\replaced[id=PD]{A}{We developed and implemented a simulation model with a}
modular event-based \replaced{simulation model was developed with}{approach,
	where} \added[id=PD]{sub-}modules \deleted[id=PD]{are} implemented on
independent time-scales appropriate to capture the characteristic of the
\replaced[id=PD]{different processes}{process modelled} (Figure 1).
\added[id=PD]{The following sub-modules were included to capture the full
	system: 1) Population dynamics, 2) Recruitment dynamics, 3) Population
	movement, 4) fishery dynamics.}\\
